General purpose gene annotation using deep learning

### 2020-04-07 paper/main.tex
dcnn values

\subsection{Dilated CNN Baseline Network Search}
\label{sec:dcnn}
\begin{table}[!t]
\processtable{Parameter search space for the dilated CNN baselines\label{tab:dcnn}} {
\begin{tabular}{@{}ll@{}}
\toprule Parameter & Possible Values \\
\midrule
Kernel Size & \{4, 8, 12, 16\}\\
Initial Filter Depth & \{32, 64, 96, 128\}\\
Number of Layers Before Doubling Filter Count & \{1, 2\}\\
Dilation Multiplier & \{2, 3\}\\
Number of Convolutional Layers & \{2, 3, 4, 5, 6, 7, 8\}\\
Number of Hidden Fully Connected (FC) Layers & \{0, 1, 2\}\\	
Dropout Used on FC Output & \{0.0, 0.01, 0.1, 0.2, 0.3\}\\
Learning Rate & \{1e-3, 1e-4\}\\

@@

\begin{table}[!t]
\processtable{Final Parameters of dilated CNN baselines\label{tab:dcnn_best}} {
\begin{tabular}{@{}lll@{}}
\toprule Parameter & Possible Animal Values & Possible Plant Values\\
\midrule
Layers & 4 & \\
Units per layer & 256 & \\
Learning rate & 1e-4 & \\
Optimizer & Adam & \\
\botrule
\end{tabular}}{The parameters of the dilated CNN model that performed the best according to the Genic F1 of the validation data of the respective training genomes. }
\end{table}

>>>>

\subsection{Dilated CNN Baseline Network Search}
\label{sec:dcnn}
\begin{table}[!t]
\processtable{Parameter search space for the dilated CNN baselines\label{tab:dcnn}} {
\begin{tabular}{@{}ll@{}}
\toprule Parameter & Possible Values \\
\midrule
Kernel Size & \{4, 8, 12, 16\}\\
Initial Filter Depth & \{32, 64, 96, 128\}\\
Number of Layers Before Doubling Filter Count & \{1, 2\}\\
Dilation Multiplier & \{2, 3\}\\
Number of Convolutional Layers & \{2, 3, 4, 5, 6, 7, 8\}\\
Number of Hidden Fully Connected (FC) Layers & \{0, 1, 2\}\\	
Dropout Used on FC and Final Conv Layer Output & \{0.0, 0.01, 0.1, 0.2, 0.3\}\\
Learning Rate & \{1e-3, 1e-4\}\\

@@

\begin{table}[!t]
\processtable{Final Parameters of dilated CNN baselines\label{tab:dcnn_best}} {
\begin{tabular}{@{}lll@{}}
\toprule Parameter & Animals & Plants\\
\midrule
Kernel Size & 16 & 16\\
Initial Filter Depth & 96 & 32\\
Number of Layers Before Doubling Filter Count & 2 & 2\\
Dilation Multiplier & 3 & 3\\
Number of Convolutional Layers & 6 & 8\\
Number of Hidden Fully Connected (FC) Layers & 2 & 0\\
Dropout Used on FC Output & 0.0 & 0.0\\
Learning Rate & 1e-4 & 1e-3\\
\botrule
\end{tabular}}{The parameters of the dilated CNN model that performed the best according to the Genic F1 of the validation data of the respective training genomes. }
\end{table}
